%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.5in,top=0.4in,right=0.5in,bottom=0.4in]{geometry} % Document margins
\usepackage{multicol}

\name{Joe Ledger} % Your name
\address{joewledger@gmail.com}
\address{(646)~$\cdot$~684~$\cdot$~2248} % Your phone number and email
\address{Cleveland, OH}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Case Western Reserve University (CWRU)} \hfill {\em Cleveland, OH} \\
M.S. in Computer Science \hfill {\em Expected Graduation: Spring 2018}\\ 
\setlength\parindent{24pt} \indent Graduate GPA: 4.0 \\
B.S. in Computer Science \hfill {\em Expected Graduation: Spring 2017}\\
\setlength\parindent{24pt} \indent Minor: Applied Data Science \\
\setlength\parindent{24pt} \indent Undergraduate GPA: 3.56 \\
{\bf Bronx High School of Science} \hfill {\em Graduated: Spring 2013}

\end{rSection}

%---------------------------------------------------------------------------------------

\begin{rSection}{Key Projects}
{\bf Cached Personalized Page Rank}
\begin{list}{$\cdot$}{\leftmargin=2em}
\vspace{-.5em}
\item A research effort to speed Personalized Page Rank using precomputed proximity vectors.
\vspace{-.5em}
\item Technologies: Java, Apache Commons Math, MySQL, Python, Matplotlib
\vspace{-.5em}
\end{list}

{\bf Cell Line Classification Project}
\begin{list}{$\cdot$}{\leftmargin=2em}
\vspace{-.5em}
\item A research effort to predict cancer cell line drug response using machine learning.
\vspace{-.5em}
\item Technologies: Python, Python Scientific Stack (Pandas, Scipy, Numpy, Matplotlib), Scikit-Learn
\vspace{-.5em}
\end{list}

{\bf Green Labs Data Visualization Application}

\begin{list}{$\cdot$}{\leftmargin=2em}
\vspace{-.5em}
\item Desktop Application for creating high quality custom visualizations from energy sensor data.
\vspace{-.5em}
\item Technologies: Qt, PyQt, Python, Pandas, Matplotlib
\vspace{-.5em}
\end{list}

{\bf UnVolt Mobile/Web Backend}
\begin{list}{$\cdot$}{\leftmargin=2em}
\vspace{-.5em}
\item Developing a backend for an Personal Energy Recommendations mobile/web application.
\vspace{-.5em}
\item Still early in development, but anticipated: Java, C, MySQL
\vspace{-.5em}
\end{list}
\end{rSection}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{CWRU Department of Computer Science}{Summers: 2015, 2016}{Undergraduate Researcher}{Cleveland, OH}{\leftmargin=2em}


\item Summer 2015: Worked on the Cell Line Classification Project
{\renewcommand\labelitemi{$\cdot$}\vspace{-0.5em}
\begin{itemize}
\item Used machine learning algorithms (Support Vector Machines and Decision Trees) to classify cell lines by their reaction to the cancer drug SMAPs using gene expression and IC50 data.
\vspace{-0.5em}  
\item Results presented at the 2015 CWRU Data Science Symposium and 2016 Research ShowCase.
\end{itemize}
}
\item Summer 2016: Working on Cached Personalized Page Rank
{\renewcommand\labelitemi{$\cdot$}\vspace{-0.5em}
\begin{itemize}
\item Effort to speed Personalized Page Rank computations by using precomputed proximity vectors.
\vspace{-0.5em}  
\item Early results are promising: 25\% speed increases for selected parameter settings.
\end{itemize}
}
\item Both Summers : Peer-reviewed papers for Academic Conferences (ACM-BCB 2015, APBC 2016)
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{CWRU Office of Sustainability}{October 2015 - May 2016 (Part Time)}{Desktop Application Developer}{Cleveland, OH}
\item Developed a desktop application with an easy-to-use GUI for non-technical users to make high-quality, fully-customizable data visualizations from energy sensors located in labs around campus. Also includes an integrated energy savings calculator.
\item Application is used by lab auditors who write reports on how behavior changes could save energy. Both visualizations and energy calculator results are included in reports.
\item Consulted with sustainability experts to determine best types of visualizations to include based on potential impact on behavioral changes.
\end{rSubsection}

\begin{rSubsection}{BldgScout Progamming Intern}{June - September 2016 (Part Time)}{Mobile/Web Backend Development}{Cleveland, OH}
\item Developing a mobile/web backend for UnVolt, an application designed to provide personalized energy saving recommendations to users based on location, personal preferences, and home characteristics.
\item Collaborating with The Form Group (who are designing the mobile frontend) on a clear, consistent, and easy to use backend API.

\end{rSubsection}

\end{rSection}

%------------------------------------------------

\begin{rSection}{Relevant Coursework}
\begin{multicols}{2}[]
\textbf{Data Mining} \\
\textbf{High Performance Scientific Computing} \\
\textbf{Causal Learning from Data} \\
\textbf{Bioinformatics for Systems Biology} \\ 
Computer Networks \\
Algorithms \\
Database Systems \\
Software Craftsmanship
\end{multicols}
\vspace{-1.0em}
*Courses in \textbf{bold} were taken at the graduate level.
\end{rSection}


%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}
\begin{list}{$\cdot$}{\leftmargin=0em}
\item Proficient with programming languages Python and Java.
\vspace{-0.5em}
\item Experience with data science tools pandas, scikit-learn, scipy, and numpy.
\vspace{-0.5em}
\item Experienced with SQL, Git, Linux Command Line, LaTeX.
\vspace{-0.5em}
\item Experience with Cross-Platform Desktop Application Development with Qt.
\vspace{-0.5em}
\end{list}
\end{rSection}

%----------------------------------------------------------------------------------------
%	HONORS AND AWARDS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Honors and Awards}
\begin{list}{$\cdot$}{\leftmargin=0em}
\item University Merit Scholarship \hfill August 2013 - Present
\vspace{-0.5em}
\item Alumni Association Outstanding Junior/Senior Scholarship \hfill Spring 2016 - Present
\vspace{-0.5em}
\item Dean's High Honor Roll \hfill Spring 2014, Fall 2014
\vspace{-0.5em}
\item Dean's Honor Roll \hfill Spring 2015, Fall 2015, Spring 2016
\vspace{-0.5em}
\item Varsity Athlete (Cross-Country, Track \& Field) for CWRU \hfill{August 2013 - Present}
\vspace{-0.5em}
\item 5x UAA All-Academic Team \hfill{Spring 2014 - Present}
\vspace{-0.5em}
\end{list}


\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
